Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}

### 2019-01-19 clustering_infinite_model.tex
Performed the splitting of cases for k and responded to/implemented several comments from Tobias.

\TM{ @Pim and @Nikolaos : if you have not done so already, can you please check the computations in section 4 very very carefully. }
In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively. This is done in several steps. Recall that for $p\in \R \times \R_+ =: \Rcal$,
\[
	\BallPo{p} = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\},
\]
denotes the neighborhood ball of $p$. Furthermore we recall the definition of $\Delta_\Pcal$ 
\[
	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
\]
where $\eta_{y} = \frac{\mu_{\alpha,\nu}|_{\BallPo{(0,y)}}}{\Mu{\BallPo{(0,y)}}}$ is the marginal probability density associated with a randomly sampled neighbor of $(0,y)$.

@@

\subsection{Degree distribution in $G_\Pcal(\alpha, \nu)$}

>>>>

\TM{ @Pim and @Nikolaos : if you have not done so already, can you please check the computations in section 4 very very carefully. }

\PvdH{@All: I haven't touched this section yet.}

In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively. This is done in several steps. Recall that for $p\in \R \times \R_+ =: \Rcal$,
\[
	\BallPo{p} = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\},
\]
denotes the neighborhood ball of $p$. Furthermore we recall the definition of $\Delta_\Pcal$ 
\[
	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
\]
where $\eta_{y} = \frac{\mu_{\alpha,\nu}|_{\BallPo{(0,y)}}}{\Mu{\BallPo{(0,y)}}}$ is the marginal probability density associated with a randomly sampled neighbor of $(0,y)$.

@@

\subsection{Degree distribution in $G_\Pcal(\alpha, \nu)$}\label{ssec:degrees_infinite_model}
